### 2022-10-23 doc/manuscript/translocation.qmd
Fix #17, change MYLF to R. sierrae

To determine the implications of acquired Bd resistance on long-term population viability, we developed a dynamic, population model for MYLF. Our central question was: how does the magnitude and variation in observed adult survival probability across translocated populations affect the long-term persistence probability of populations? We developed a model that tracked seven state variables of an MYLF population: the density of translocated adults ($A_T$), the density of adults naturally recruited into the population ($A_R$), the density of first year larvae ($L_1$), the density of second year larvae ($L_2$), the density of third year larvae ($L_3$), the density of first year juveniles ($J_1$), and the density of second year juveniles ($J_2$). We divided adults into two classes $A_T$ and $A_R$ because there was evidence that the survival probability of translocated adults and naturally recruited adults differed.

>>>>

To determine the implications of acquired Bd resistance on long-term population viability, we developed a dynamic, population model for *R. sierrae*. Our central question was: how does the magnitude and variation in observed adult survival probability across translocated populations affect the long-term persistence probability of populations? We developed a model that tracked seven state variables of a *R. sierrae* population: the density of translocated adults ($A_T$), the density of adults naturally recruited into the population ($A_R$), the density of first year larvae ($L_1$), the density of second year larvae ($L_2$), the density of third year larvae ($L_3$), the density of first year juveniles ($J_1$), and the density of second year juveniles ($J_2$). We divided adults into two classes $A_T$ and $A_R$ because there was evidence that the survival probability of translocated adults and naturally recruited adults differed.
